### 2017-09-29 pages/math/calc-3/quiz-generator/in/exam01-practice.tex
Update!

::: Math-252 Practice Exam 1
% 1, 2, 3, 4, 5
Using \(\vec u=\langle-4,6,5\rangle\) and \(\vec v=\langle 2,-3,1\rangle\),
\begin{enumerate}[a.]
  \item Find \(\|\vec u\|\) and \(\|\vec v\|\).
  \item Find \(\vec u\cdot\vec v\).
  \item Find the angle \(\theta\) between \(\vec u\) and \(\vec v\).
  \item Find \(\text{proj}_{\vec v}\vec u\).
  \item Find \(\vec u\times\vec v\).
\end{enumerate}
===
\begin{enumerate}[a.]
  \item
    \(\begin{aligned}[t]
      \|\vec u\|&=\sqrt{77} \\
      \|\vec v\|&=\sqrt{14}
    \end{aligned}\)
  \item \(\vec u\cdot\vec v=-21\)
  \item \(\theta=\arccos\left(\frac{-21}{7\sqrt{22}}\right)\)
\end{enumerate}
---
% 6, 7, 8, 9
Using \(P(-4,1,2)\), \(Q(1,-3,4)\), \(R(-1,0,2)\),
\begin{enumerate}[a.]
  \item Find an equation of the plane passing through the points.
  \item Find parametric equations for the line through P and parallel to \(a=\langle 2,-1,4\rangle\).
  \item Find the distance from the point \((5,-3,2)\) to the plane.
  \item Find the area of the parallelogram determined by \(P\), \(Q\), and \(R\).
\end{enumerate}
===
\begin{enumerate}[a.]
  \item \(2x+6y+7z-12=0\)
  \item \(x=2t-4,\ y=-t+1,\ z=4t+2\)
  \item \(D=\frac{6}{\sqrt{89}}\)
  \item \(A=\sqrt{89}\)
\end{enumerate}
---
% 10
Identify the surface \(x=y^2\).
===
Parabolic cylinder
---
% 11
Identify the surface \(4x^2+4y^2+z^2=4\).
===
ANSWER
---
% 12
Identify the surface \(2x^2-3y^2+6z^2=6\).
===
ANSWER
---
% 13
Identify the surface \(x^2-6y+5z^2=0\).
===
ANSWER
---
% 14, 15, 16, 17
A baseball is thrown from the stands 128 feet above the field at an angle of
30 degrees up from the horizontal with an initial speed of 64 feet per second.
\begin{enumerate}[a.]
  \item Give the position vector for any time \(t\).
  \item When will the ball strike the ground?
  \item How far away will the ball strike the ground?
  \item What is the speed of the ball when it strikes the ground?
\end{enumerate}
===
ANSWER
---
% 18, 19, 20, 21
Using \(\vec r(t)=\langle t\cos t,t\sin t,t^2\rangle\) at \(t=0\),
\begin{enumerate}[a.]
  \item Find \(\vec v\) and \(\vec a\).
  \item Find \(\vec T\) and \(\vec N\).
  \item Find \(K\).
  \item By first finding \(a_{\vec T}\) and \(a_{\vec N}\),\\
    express \(a=a_{\vec T}\vec T+a_{\vec N}\vec N\).
\end{enumerate}
===
\begin{enumerate}[a.]
  \item
    \(\begin{aligned}[t]
      \vec v&=\langle-t\sin t+\cos t,t\cos t+\sin t,2t\rangle \\
      \vec a&=\langle-t\cos t-2\sin t,-t\sin t+2\cos t,2\rangle
    \end{aligned}\)
  \item
    \(\begin{aligned}[t]
      \|\vec v\|&=\frac{}{} \\
      \vec T&= \\
      \vec N&=
    \end{aligned}\)
\end{enumerate}

>>>>

::: M[label=\alph*.]th-252 Pr[label=\alph*.]ctice Ex[label=\alph*.]m 1
% 1, 2, 3, 4, 5
Using \(\vec u=\l[label=\alph*.]ngle-4,6,5\r[label=\alph*.]ngle\) [label=\alph*.]nd \(\vec v=\l[label=\alph*.]ngle 2,-3,1\r[label=\alph*.]ngle\),
\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
  \item Find \(\|\vec u\|\) [label=\alph*.]nd \(\|\vec v\|\)[label=\alph*.]
  \item Find \(\vec u\cdot\vec v\)[label=\alph*.]
  \item Find the [label=\alph*.]ngle \(\thet[label=\alph*.]\) between \(\vec u\) [label=\alph*.]nd \(\vec v\)[label=\alph*.]
  \item Find \(\text{proj}_{\vec v}\vec u\)[label=\alph*.]
  \item Find \(\vec u\times\vec v\)[label=\alph*.]
\end{enumer[label=\alph*.]te}
===
\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
  \item
    \(\begin{[label=\alph*.]ligned}[t]
      \|\vec u\|&=\sqrt{77} \\
      \|\vec v\|&=\sqrt{14}
    \end{[label=\alph*.]ligned}\)
  \item \(\vec u\cdot\vec v=-21\)
  \item \(\displ[label=\alph*.]ystyle \thet[label=\alph*.]=\[label=\alph*.]rccos\left(\fr[label=\alph*.]c{-21}{7\sqrt{22}}\right)\)
\end{enumer[label=\alph*.]te}
---
% 6, 7, 8, 9
Using \(P(-4,1,2)\), \(Q(1,-3,4)\), \(R(-1,0,2)\),
\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
  \item Find [label=\alph*.]n equ[label=\alph*.]tion of the pl[label=\alph*.]ne p[label=\alph*.]ssing through the points[label=\alph*.]
  \item Find p[label=\alph*.]r[label=\alph*.]metric equ[label=\alph*.]tions for the line through P [label=\alph*.]nd p[label=\alph*.]r[label=\alph*.]llel to \([label=\alph*.]=\l[label=\alph*.]ngle 2,-1,4\r[label=\alph*.]ngle\)[label=\alph*.]
  \item Find the dist[label=\alph*.]nce from the point \((5,-3,2)\) to the pl[label=\alph*.]ne[label=\alph*.]
  \item Find the [label=\alph*.]re[label=\alph*.] of the p[label=\alph*.]r[label=\alph*.]llelogr[label=\alph*.]m determined by \(P\), \(Q\), [label=\alph*.]nd \(R\)[label=\alph*.]
\end{enumer[label=\alph*.]te}
===
\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
  \item \(2x+6y+7z-12=0\)
  \item \(x=2t-4,\ y=-t+1,\ z=4t+2\)
  \item \(\displ[label=\alph*.]ystyle D=\fr[label=\alph*.]c{6}{\sqrt{89}}\)
  \item \(A=\sqrt{89}\)
\end{enumer[label=\alph*.]te}
---
% 10
Identify the surf[label=\alph*.]ce \(x=y^2\)[label=\alph*.]
===
P[label=\alph*.]r[label=\alph*.]bolic cylinder
---
% 11
Identify the surf[label=\alph*.]ce \(4x^2+4y^2+z^2=4\)[label=\alph*.]
===
Circul[label=\alph*.]r ellipsoid
---
% 12
Identify the surf[label=\alph*.]ce \(2x^2-3y^2+6z^2=6\)[label=\alph*.]
===
Hyperb[label=\alph*.]loid (one sheet)
---
% 13
Identify the surf[label=\alph*.]ce \(x^2-6y+5z^2=0\)[label=\alph*.]
===
Elliptic[label=\alph*.]l cone
---
% 14, 15, 16, 17
A b[label=\alph*.]seb[label=\alph*.]ll is thrown from the st[label=\alph*.]nds 128 feet [label=\alph*.]bove the field [label=\alph*.]t [label=\alph*.]n [label=\alph*.]ngle of
30 degrees up from the horizont[label=\alph*.]l with [label=\alph*.]n initi[label=\alph*.]l speed of 64 feet per second[label=\alph*.]
\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
  \item Give the position vector for [label=\alph*.]ny time \(t\)[label=\alph*.]
  \item When will the b[label=\alph*.]ll strike the ground?
  \item How f[label=\alph*.]r [label=\alph*.]w[label=\alph*.]y will the b[label=\alph*.]ll strike the ground?
  \item Wh[label=\alph*.]t is the speed of the b[label=\alph*.]ll when it strikes the ground?
\end{enumer[label=\alph*.]te}
===
\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
  \item \(\vec r(t)=\l[label=\alph*.]ngle 32\sqrt 3t,-16t^2+32t+128\r[label=\alph*.]ngle\)
  \item in 4 seconds
  \item \(128\sqrt 3\) feet [label=\alph*.]w[label=\alph*.]y
  \item \(64\sqrt 3\) feet per second
\end{enumer[label=\alph*.]te}
---
% 18, 19, 20, 21
Using \(\vec r(t)=\l[label=\alph*.]ngle t\cos t,t\sin t,t^2\r[label=\alph*.]ngle\) [label=\alph*.]t \(t=0\),
\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
  \item Find \(\vec v\) [label=\alph*.]nd \(\vec [label=\alph*.]\)[label=\alph*.]
  \item Find \(\vec T\) [label=\alph*.]nd \(\vec N\)[label=\alph*.]
  \item Find \(K\)[label=\alph*.]
  \item By first finding \([label=\alph*.]_{\vec T}\) [label=\alph*.]nd \([label=\alph*.]_{\vec N}\),\\
    express \([label=\alph*.]=[label=\alph*.]_{\vec T}\vec T+[label=\alph*.]_{\vec N}\vec N\)[label=\alph*.]
\end{enumer[label=\alph*.]te}
===
\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
  \item
    \(\begin{[label=\alph*.]ligned}[t]
      \vec v&=\l[label=\alph*.]ngle-t\sin t+\cos t,t\cos t+\sin t,2t\r[label=\alph*.]ngle \\
      \vec [label=\alph*.]&=\l[label=\alph*.]ngle-t\cos t-2\sin t,-t\sin t+2\cos t,2\r[label=\alph*.]ngle
    \end{[label=\alph*.]ligned}\)
  \item \(
    \displ[label=\alph*.]ystyle \begin{[label=\alph*.]ligned}[t]
      \vec T&=\left\l[label=\alph*.]ngle
        \fr[label=\alph*.]c{-t\sin 5+\cos t}{\sqrt{5t^2+1}},
        \fr[label=\alph*.]c{t\cos t+\sin 5}{\sqrt{5t^2+1}},
        \fr[label=\alph*.]c{2t}{\sqrt{5t^2+1}}\right\r[label=\alph*.]ngle\\
      \vec N&=\left\l[label=\alph*.]ngle\right\r[label=\alph*.]ngle
    \end{[label=\alph*.]ligned}\)
  \item \(
    \displ[label=\alph*.]ystyle K(0)=
\end{enumer[label=\alph*.]te}
